##Library innitialization
```{r}
library(TCGAbiolinks)
library(SummarizedExperiment)
library(data.table)
library(dplyr)
library(DT)
library(survival)


#library("categoryCompare")
#library("GO.db")
#library("KEGG.db")

```


##Import Corex Group Information, Write groups for annotation
```{r}
#workingDir<-"LinearCorex/out/LUADGeneTableDE0_200_1_40/"
#workingDir<-"LinearCorex/out/LUADGeneTable0_200_1_40/"
#workingDir<-"LinearCorex/out/LUADGeneTableDE0_100_1_20/"
#workingDir<-"LinearCorex/out/2LUADGeneTableDE0_200_1_40/"
#workingDir<-"Corex/out/LUADGeneTableLFC2_hidden3_0_100_1_20/"
workingDir<-"Corex/out/LUADGeneTable_hidden3_0_200_1_40/"

#Import linear corex groups
corexGroups<-read.table(file = paste0(workingDir,"corexGroups.csv"), sep = ",", header=TRUE, row.names=1)
mis<-read.table(file = paste0(workingDir,"mis.csv"), sep = ",", header=TRUE, row.names=1)
alpha<-read.table(file = paste0(workingDir,"alpha.csv"), sep = ",", header=TRUE, row.names=1)


#FIND MAF
#MAFIndex<-grep("ENSG00000178573",row.names(corexGroups))
#corexGroups[MAFIndex,]
#corexGroups[which(corexGroups$group0==195),]

#which(corexGroups[which(corexGroups$group0==0),]$mI1>0.25)
```

##Load custom annotations from biomart, annotate with TopGo
```{r}
library(biomaRt)
library(org.Hs.eg.db)
library(topGO)
library(GO.db)

bm <- useMart("ensembl")
bm <- useDataset("hsapiens_gene_ensembl", mart=bm)

listAttributes(bm)
listFilters(bm)

test<-rownames(corexGroups[1,])
test
# Get ensembl gene ids and GO terms
EG2GO <- getBM(mart=bm,
               attributes=c('ensembl_gene_id','go_id','description')
               )

listAttributes(bm)

#OR
#bm=useMart(biomart="ensembl", dataset="hsapiens_gene_ensembl")
#EG2GO = getBM(mart = bm,attributes=c('ensembl_gene_id','go_id'))

# Remove blank entries
EG2GO <- EG2GO[EG2GO$go_id != '',]

# convert from table format to list format
geneID2GO <- by(EG2GO$go_id,
                EG2GO$ensembl_gene_id,
                function(x) as.character(x))
```

##TopGo Annotation of each corex layer 0 Group
```{r}
dir.create(paste0(workingDir,"annotations"))

for(ii in 0:max(corexGroups[,1])){
groupTemp<-corexGroups[which(corexGroups$group0==ii),]
inSelection = row.names(groupTemp)
inUniverse = row.names(dataPrep2)
alg <- ifelse(inUniverse %in% inSelection, 1, 0)
names(alg) <- inUniverse

GOdata <- new("topGOdata", description="My project", ontology="BP", allGenes=alg, geneSel = function(b) {return(b == 1)}, annot = annFUN.gene2GO, gene2GO = geneID2GO)

write(paste0(ii,": ",numSigGenes(GOdata),"/",length(inSelection)),file=paste0(workingDir,"annotations/numGenesannotated.txt"), append=TRUE)

resultFisher <- runTest(GOdata, algorithm = "weight01", statistic = "fisher")

topTable<-GenTable(GOdata, classicFisher = resultFisher, topNodes = 200)

#showSigOfNodes(GOdata, score(resultFisher), firstSigNodes = 3, useInfo ='all')
#printGraph(GOdata, resultFisher, firstSigNodes = 3, fn.prefix = paste0("corexOutputs/layer0GOGraphs/topGraph",toString(ii)), useInfo = "all", pdfSW = TRUE)

write.table(topTable, file = paste0(paste0(workingDir,"annotations/topTable"),toString(ii),".csv"), sep = ",", col.names = NA, qmethod = "double")
}
```

##TopGo Annotation of each corex layer 0 Group mis
```{r}
workingDir2=paste0(workingDir,"annotationsMis0p05/")
dir.create(workingDir2)

for(ii in 1:length(mis[1,])){
groupTemp<-mis[which(mis[,ii]>0.05),]
inSelection = row.names(groupTemp)
inUniverse = row.names(dataPrep2)
alg <- ifelse(inUniverse %in% inSelection, 1, 0)
names(alg) <- inUniverse

GOdata <- new("topGOdata", description="My project", ontology="BP", allGenes=alg, geneSel = function(b) {return(b == 1)}, annot = annFUN.gene2GO, gene2GO = geneID2GO)

write(paste0(ii-1,": ",numSigGenes(GOdata),"/",length(inSelection)),file=paste0(workingDir2,"numGenesannotated.txt"), append=TRUE)

resultFisher <- runTest(GOdata, algorithm = "weight01", statistic = "fisher")

topTable<-GenTable(GOdata, classicFisher = resultFisher, topNodes = 200)

#showSigOfNodes(GOdata, score(resultFisher), firstSigNodes = 3, useInfo ='all')
#printGraph(GOdata, resultFisher, firstSigNodes = 3, fn.prefix = paste0("corexOutputs/layer0GOGraphs/topGraph",toString(ii)), useInfo = "all", pdfSW = TRUE)

write.table(topTable, file = paste0(paste0(workingDir2,"topTable"),toString(ii-1),".csv"), sep = ",", col.names = NA, qmethod = "double")
}
```

##TopGo Annotation of each corex layer 0 Group mis
```{r}
workingDir2=paste0(workingDir,"annotationsMis0p1/")
dir.create(workingDir2)

for(ii in 1:length(mis[1,])){
groupTemp<-mis[which(mis[,ii]>0.1),]
inSelection = row.names(groupTemp)
inUniverse = row.names(dataPrep2)
alg <- ifelse(inUniverse %in% inSelection, 1, 0)
names(alg) <- inUniverse

GOdata <- new("topGOdata", description="My project", ontology="BP", allGenes=alg, geneSel = function(b) {return(b == 1)}, annot = annFUN.gene2GO, gene2GO = geneID2GO)

write(paste0(ii-1,": ",numSigGenes(GOdata),"/",length(inSelection)),file=paste0(workingDir2,"numGenesannotated.txt"), append=TRUE)

resultFisher <- runTest(GOdata, algorithm = "weight01", statistic = "fisher")

topTable<-GenTable(GOdata, classicFisher = resultFisher, topNodes = 200)

#showSigOfNodes(GOdata, score(resultFisher), firstSigNodes = 3, useInfo ='all')
#printGraph(GOdata, resultFisher, firstSigNodes = 3, fn.prefix = paste0("corexOutputs/layer0GOGraphs/topGraph",toString(ii)), useInfo = "all", pdfSW = TRUE)

write.table(topTable, file = paste0(paste0(workingDir2,"topTable"),toString(ii-1),".csv"), sep = ",", col.names = NA, qmethod = "double")
}
```

##TopGo Annotation of each corex layer 0 Group alpha
```{r}
dir.create(paste0(workingDir,"annotationsAlpha"))

for(ii in 1:length(alpha[1,])){
groupTemp<-alpha[which(alpha[,ii]>0.01),]
inSelection = row.names(groupTemp)
inUniverse = row.names(dataPrep2)
alg <- ifelse(inUniverse %in% inSelection, 1, 0)
names(alg) <- inUniverse

GOdata <- new("topGOdata", description="My project", ontology="BP", allGenes=alg, geneSel = function(b) {return(b == 1)}, annot = annFUN.gene2GO, gene2GO = geneID2GO)

write(paste0(ii-1,": ",numSigGenes(GOdata),"/",length(inSelection)),file=paste0(workingDir,"annotationsAlpha/numGenesannotated.txt"), append=TRUE)

resultFisher <- runTest(GOdata, algorithm = "weight01", statistic = "fisher")

topTable<-GenTable(GOdata, classicFisher = resultFisher, topNodes = 200)

#showSigOfNodes(GOdata, score(resultFisher), firstSigNodes = 3, useInfo ='all')
#printGraph(GOdata, resultFisher, firstSigNodes = 3, fn.prefix = paste0("corexOutputs/layer0GOGraphs/topGraph",toString(ii)), useInfo = "all", pdfSW = TRUE)

write.table(topTable, file = paste0(paste0(workingDir,"annotationsAlpha/topTable"),toString(ii-1),".csv"), sep = ",", col.names = NA, qmethod = "double")
}

```

##Make a file with gene names and descrptions for each group
```{r}
# Get ensembl gene ids and GO terms
EGWD <- getBM(mart=bm,attributes=c('ensembl_gene_id','external_gene_name','description'))

dir.create(paste0(workingDir,"descriptions"))
for(ii in 0:max(corexGroups[,1])){
groupTemp<-corexGroups[which(corexGroups$group0==ii),]
write.table(EGWD[EGWD$ensembl_gene_id%in%rownames(groupTemp),], file = paste0(paste0(workingDir,"descriptions/group0_"),toString(ii),".txt"),quote=FALSE, row.names=FALSE, col.names=FALSE, sep ="\t")
}

dir.create(paste0(workingDir,"descriptionsMis0p1"))
for(ii in 1:length(mis[1,])){
groupTemp<-mis[which(mis[,ii]>0.1),]
write.table(EGWD[EGWD$ensembl_gene_id%in%rownames(groupTemp),], file = paste0(paste0(workingDir,"descriptionsMis0p1/group0_"),toString(ii-1),".txt"),quote=FALSE, row.names=FALSE, col.names=FALSE, sep ="\t")
write(length(rownames(groupTemp)),file=paste0(workingDir,"descriptionsMis0p1/numGenes.txt"), append=TRUE)
}

dir.create(paste0(workingDir,"descriptionsAlpha"))
for(ii in 1:length(alpha[1,])){
groupTemp<-alpha[which(alpha[,ii]>0.01),]
write.table(EGWD[EGWD$ensembl_gene_id%in%rownames(groupTemp),], file = paste0(paste0(workingDir,"descriptionsAlpha/group0_"),toString(ii-1),".txt"),quote=FALSE, row.names=FALSE, col.names=FALSE, sep ="\t")
write(length(rownames(groupTemp)),file=paste0(workingDir,"descriptionsAlpha/numGenes.txt"), append=TRUE)
}
```

##Make a file with Ensemble ids for each group for Panther
```{r}
dir.create(paste0(workingDir,"layer0IDs"))
for(ii in 0:max(corexGroups[,1])){
outfile0<-paste0(paste0(workingDir,"layer0IDs/group0_"),toString(ii),".txt")
group0Temp<-corexGroups[which(corexGroups$group0==ii),]
write.table(rownames(group0Temp), file = outfile0, quote=FALSE, row.names=FALSE, col.names=FALSE)
}

dir.create(paste0(workingDir,"layer0IDsMis"))
for(ii in 1:length(mis[1,])){
outfile0<-paste0(paste0(workingDir,"layer0IDsMis/group0_"),toString(ii-1),".txt")
group0Temp<-mis[which(mis[,ii]>0.05),]
write.table(rownames(group0Temp), file = outfile0, quote=FALSE, row.names=FALSE, col.names=FALSE)
}

dir.create(paste0(workingDir,"layer0IDsAlpha"))
for(ii in 1:length(alpha[1,])){
outfile0<-paste0(paste0(workingDir,"layer0IDsAlpha/group0_"),toString(ii-1),".txt")
group0Temp<-alpha[which(alpha[,ii]>0.01),]
write.table(rownames(group0Temp), file = outfile0, quote=FALSE, row.names=FALSE, col.names=FALSE)
}


```
