##Library innitialization
```{r}
library(TCGAbiolinks)
library(SummarizedExperiment)
library(data.table)
library(dplyr)
library(DT)
library(survival)


library(biomaRt)
library(org.Hs.eg.db)
library(topGO)
library(GO.db)

```


##Import Corex Group Information, Write groups for annotation
```{r}
#workingDir<-"Corex/out/LUADGeneTable_hidden3_0_200_1_40/"
workingDir<-"LinearCorex/out/LUADGeneTableVST0_200_1_40/"
#workingDir<-"LinearCorex/out/LUADGeneTableVST0_100_1_20/"
#workingDir<-"LinearCorex/out/LUADGeneTableVST0_400_1_80/"

#Import linear corex groups
corexGroups<-read.table(file = paste0(workingDir,"corexGroups.csv"), sep = ",", header=TRUE, row.names=1)
#mis<-read.table(file = paste0(workingDir,"mis.csv"), sep = ",", header=TRUE, row.names=1)

#FIND MAF
#MAFIndex<-grep("ENSG00000178573",row.names(corexGroups))
#corexGroups[MAFIndex,]
#corexGroups[which(corexGroups$group0==195),]

#which(corexGroups[which(corexGroups$group0==0),]$mI1>0.25)
```

##Load custom annotations from biomart, annotate with TopGo
```{r}
bm <- useMart("ensembl")
bm <- useDataset("hsapiens_gene_ensembl", mart=bm)

listAttributes(bm)
listFilters(bm)

test<-rownames(corexGroups[1,])
test
# Get ensembl gene ids and GO terms
EG2GO <- getBM(mart=bm,
               attributes=c('ensembl_gene_id','go_id','description')
               )

listAttributes(bm)

#OR
#bm=useMart(biomart="ensembl", dataset="hsapiens_gene_ensembl")
#EG2GO = getBM(mart = bm,attributes=c('ensembl_gene_id','go_id'))

# Remove blank entries
EG2GO <- EG2GO[EG2GO$go_id != '',]

# convert from table format to list format
geneID2GO <- by(EG2GO$go_id,
                EG2GO$ensembl_gene_id,
                function(x) as.character(x))
```

##TopGo Annotation of each corex layer 0 Group
```{r}

dir.create(paste0(workingDir,"annotations"))

for(ii in 0:max(corexGroups[,1])){
#for(ii in c(6,9,15,16,22,33,75,111,163,272,309,314,380)){
groupTemp<-corexGroups[which(corexGroups$group0==ii),]
inSelection = row.names(groupTemp)
inUniverse = row.names(dataPrep2)
alg <- ifelse(inUniverse %in% inSelection, 1, 0)
names(alg) <- inUniverse

GOdata <- new("topGOdata", description="My project", ontology="BP", allGenes=alg, geneSel = function(b) {return(b == 1)}, annot = annFUN.gene2GO, gene2GO = geneID2GO)

write(paste0(ii,": ",numSigGenes(GOdata),"/",length(inSelection)),file=paste0(workingDir,"annotations/numGenesannotated.txt"), append=TRUE)

resultFisher <- runTest(GOdata, algorithm = "weight01", statistic = "fisher")

topTable<-GenTable(GOdata, classicFisher = resultFisher, topNodes = 200)

#showSigOfNodes(GOdata, score(resultFisher), firstSigNodes = 3, useInfo ='all')
#printGraph(GOdata, resultFisher, firstSigNodes = 3, fn.prefix = paste0("corexOutputs/layer0GOGraphs/topGraph",toString(ii)), useInfo = "all", pdfSW = TRUE)


write.table(topTable, file = paste0(paste0(workingDir,"annotations/topTable"),toString(ii),".csv"), sep = ",", col.names = NA, qmethod = "double")

write(paste0(ii,": ",topTable[c(1,2),c(2,6)]),file=paste0(workingDir,"annotations/topAnnotation.txt"), append=TRUE)

}
```

##annotation enrichment from clusterProfiler
```{r}
library(clusterProfiler)
library(ReactomePA)
library(org.Hs.eg.db)
library(DOSE)

keytypes(org.Hs.eg.db)


groupTemp<-corexGroups[which(corexGroups$group0==14),]
inSelection = row.names(groupTemp)
inUniverse = row.names(dataPrep2)

eg = bitr(inSelection, fromType="ENSEMBL", toType="ENTREZID", OrgDb="org.Hs.eg.db")
eu = bitr(inUniverse, fromType="ENSEMBL", toType="ENTREZID", OrgDb="org.Hs.eg.db")

unique(eu$ENTREZID)

length(inSelection)

eg$ENTREZID

w <- enrichGO(gene = eg$ENTREZID,
                OrgDb         = org.Hs.eg.db,
                keyType       = 'ENTREZID',
                ont           = "BP",
                pAdjustMethod = "BH",
                universe = eu$ENTREZID,
                pvalueCutoff  = 0.01,
                qvalueCutoff  = 0.05)

setReadable(w, 'org.Hs.eg.db')

wdf<-as.data.frame(w)

wdf

x <- enrichPathway(gene=eg$ENTREZID,pvalueCutoff=0.1,universe = eu$ENTREZID)

setReadable(x, 'org.Hs.eg.db')
xdf<-as.data.frame(x)
xdf


y <- enrichKEGG(gene=eg$ENTREZID,
                 organism='hsa',
                 pvalueCutoff=0.05)
setReadable(y, 'org.Hs.eg.db')

ydf<-as.data.frame(y)
ydf

z <- enrichDO(gene=eg$ENTREZID,pvalueCutoff=0.1,universe = eu$ENTREZID)
setReadable(z, 'org.Hs.eg.db')
zdf<-as.data.frame(z)

zdf

ncg <- enrichNCG(gene=eg$ENTREZID,pvalueCutoff=0.1,universe = eu$ENTREZID)
setReadable(ncg, 'org.Hs.eg.db')
ncgdf<-as.data.frame(setReadable(ncg, 'org.Hs.eg.db'))

ncgdf

```

```{r}

dir.create(paste0(workingDir,"annotationsClusterProfiler"))

for(ii in 0:max(corexGroups[,1])){
#for(ii in c(13,14)){
groupTemp<-corexGroups[which(corexGroups$group0==ii),]
inSelection = row.names(groupTemp)
inUniverse = row.names(dataPrep2)

eg = bitr(inSelection, fromType="ENSEMBL", toType="ENTREZID", OrgDb="org.Hs.eg.db")
eu = bitr(inUniverse, fromType="ENSEMBL", toType="ENTREZID", OrgDb="org.Hs.eg.db")

w <- enrichGO(gene = eg$ENTREZID,
                OrgDb         = org.Hs.eg.db,
                keyType       = 'ENTREZID',
                ont           = "BP",
                pAdjustMethod = "BH",
                universe = eu$ENTREZID,
                pvalueCutoff  = 0.01,
                qvalueCutoff  = 0.05,
                readable=TRUE)
wdf<-as.data.frame(w)
write.table(wdf, file = paste0(paste0(workingDir,"annotationsClusterProfiler/go"),toString(ii),".csv"), sep = ",", col.names = NA, qmethod = "double")
write(paste0(ii,":",wdf[1,2]),file=paste0(workingDir,"annotationsClusterProfiler/topAnnotations.txt"), append=TRUE)

x <- enrichPathway(gene=eg$ENTREZID,pvalueCutoff=0.1,universe = eu$ENTREZID, readable=T)
xdf<-as.data.frame(x)
xdf
write.table(xdf, file = paste0(paste0(workingDir,"annotationsClusterProfiler/reactome"),toString(ii),".csv"), sep = ",", col.names = NA, qmethod = "double")

y <- enrichKEGG(gene=eg$ENTREZID,
                organism='hsa',
                universe = eu$ENTREZID,
                pvalueCutoff=0.05)
ydf<-as.data.frame(y)
ydf
write.table(ydf, file = paste0(paste0(workingDir,"annotationsClusterProfiler/kegg"),toString(ii),".csv"), sep = ",", col.names = NA, qmethod = "double")

z <- enrichDO(gene=eg$ENTREZID,universe=eu$ENTREZID,pvalueCutoff=0.05)
zdf<-as.data.frame(z)
zdf
write.table(zdf, file = paste0(paste0(workingDir,"annotationsClusterProfiler/do"),toString(ii),".csv"), sep = ",", col.names = NA, qmethod = "double")


}
```

##TopGo Annotation of each corex layer 0 Group mis
```{r}
workingDir2=paste0(workingDir,"annotationsMis0p15/")
dir.create(workingDir2)
#for(ii in 1:length(mis[1,])){
for(ii in 1+c(6,9,15,16,22,33,75,111,163,272,309,314,380)){
groupTemp<-mis[which(mis[,ii]>0.15),]
inSelection = row.names(groupTemp)
inUniverse = row.names(dataPrep2)
alg <- ifelse(inUniverse %in% inSelection, 1, 0)
names(alg) <- inUniverse

GOdata <- new("topGOdata", description="My project", ontology="BP", allGenes=alg, geneSel = function(b) {return(b == 1)}, annot = annFUN.gene2GO, gene2GO = geneID2GO)

write(paste0(ii-1,": ",numSigGenes(GOdata),"/",length(inSelection)),file=paste0(workingDir2,"numGenesannotated.txt"), append=TRUE)

resultFisher <- runTest(GOdata, algorithm = "weight01", statistic = "fisher")

topTable<-GenTable(GOdata, classicFisher = resultFisher, topNodes = 200)

#showSigOfNodes(GOdata, score(resultFisher), firstSigNodes = 3, useInfo ='all')
#printGraph(GOdata, resultFisher, firstSigNodes = 3, fn.prefix = paste0("corexOutputs/layer0GOGraphs/topGraph",toString(ii)), useInfo = "all", pdfSW = TRUE)

write.table(topTable, file = paste0(paste0(workingDir2,"topTable"),toString(ii-1),".csv"), sep = ",", col.names = NA, qmethod = "double")
}
```



##Make a file with gene names and descrptions for each group
```{r}
# Get ensembl gene ids and GO terms
EGWD <- getBM(mart=bm,attributes=c('ensembl_gene_id','external_gene_name','description'))

dir.create(paste0(workingDir,"descriptions"))
for(ii in 0:max(corexGroups[,1])){
groupTemp<-corexGroups[which(corexGroups$group0==ii),]
write.table(EGWD[EGWD$ensembl_gene_id%in%rownames(groupTemp),], file = paste0(paste0(workingDir,"descriptions/group0_"),toString(ii),".txt"),quote=FALSE, row.names=FALSE, col.names=FALSE, sep ="\t")
write(length(rownames(groupTemp)),file=paste0(workingDir,"descriptions/numGenes.txt"), append=TRUE)
}

length(mis[1,])

dir.create(paste0(workingDir,"descriptionsMis0p15"))
for(ii in 1:length(mis[1,])){
groupTemp<-mis[which(mis[,ii]>0.15),]
write.table(EGWD[EGWD$ensembl_gene_id%in%rownames(groupTemp),], file = paste0(paste0(workingDir,"descriptionsMis0p15/group0_"),toString(ii-1),".txt"),quote=FALSE, row.names=FALSE, col.names=FALSE, sep ="\t")
write(length(rownames(groupTemp)),file=paste0(workingDir,"descriptionsMis0p15/numGenes.txt"), append=TRUE)
}
```
##Compare groups
```{r}

g1<-read.table(file = "LinearCorex/out/LUADGeneTableVST0_200_1_40/descriptions/group0_13.txt", sep = "\t", header=FALSE, row.names=1)

g2<-read.table(file = "LinearCorex/out/LUADGeneTableVST0_100_1_20/descriptions/group0_9.txt", sep = "\t", header=FALSE, row.names=1)

length(rownames(g1))
length(rownames(g2))
length(which(rownames(g2)%in%rownames(g1)))
length(which(rownames(g1)%in%rownames(g2)))

```

##Make a file with Ensemble ids for each group for Panther
```{r}
dir.create(paste0(workingDir,"layer0IDs"))
for(ii in 0:max(corexGroups[,1])){
outfile0<-paste0(paste0(workingDir,"layer0IDs/group0_"),toString(ii),".txt")
group0Temp<-corexGroups[which(corexGroups$group0==ii),]
write.table(rownames(group0Temp), file = outfile0, quote=FALSE, row.names=FALSE, col.names=FALSE)
}

dir.create(paste0(workingDir,"layer0IDsMis"))
for(ii in 1:length(mis[1,])){
outfile0<-paste0(paste0(workingDir,"layer0IDsMis/group0_"),toString(ii-1),".txt")
group0Temp<-mis[which(mis[,ii]>0.05),]
write.table(rownames(group0Temp), file = outfile0, quote=FALSE, row.names=FALSE, col.names=FALSE)
}

dir.create(paste0(workingDir,"layer0IDsAlpha"))
for(ii in 1:length(alpha[1,])){
outfile0<-paste0(paste0(workingDir,"layer0IDsAlpha/group0_"),toString(ii-1),".txt")
group0Temp<-alpha[which(alpha[,ii]>0.01),]
write.table(rownames(group0Temp), file = outfile0, quote=FALSE, row.names=FALSE, col.names=FALSE)
}


```
